### 2019-04-26 README.Rmd
more readme fixes

Once you have downloaded and extracted the compendium, you can open [the project](vmacfeaturesearch.Rproj) with RStudio, and knit [analysis_report.Rmd](analysis/analysis_report.Rmd) to produce a report containing all statistical analyses contained in our preprint. You can also knit [paper.Rmd](analysis/paper/paper.Rmd) to produce a reproducible copy of the preprint.

>>>>

Once you have downloaded and extracted the compendium, you can open [the project](vmacfeaturesearch.Rproj) with RStudio, and knit [analysis_report.rmd](analysis/analysis_report.rmd) to produce a report containing all statistical analyses contained in our preprint. You can also knit [paper.Rmd](analysis/paper/paper.Rmd) to produce a reproducible copy of the preprint.
